### 2021-11-06 notes/scratch1.tex
scratch

\newcommand{\rname}[1]{\textsc{\footnotesize #1}}
\newcommand{\utype}{:_{\scriptscriptstyle U}}
\newcommand{\ltype}{:_{\scriptscriptstyle L}}
\newcommand{\stype}{:_s}
\newcommand{\ucons}{constructor_{\scriptscriptstyle U}}
\newcommand{\lcons}{constructor_{\scriptscriptstyle L}}
\newcommand{\scons}{constructor_{s}}
\newcommand{\pure}[1]{|#1|}

@@

  \inferrule
  { arity(A, s) }
  { arity((x \utype M) \rightarrow A, s)}
  \rname{ar-arrow}
\end{mathpar}

\subsection{Strict Positivity}
For some type $P$ and type variable $X$, the judgment $postive(P, X)$ is inductively defined over the structure of $P$ as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ X \notin m_i }
  { postive(X\ m_1...m_n, X) }
  \rname{pos-x}

@@

\subsection{Non-Linear Constructor}
For some type $C$ and type variable $X$, the judgment $\ucons(C, X)$ is inductively defined over the structure of $C$ as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ X \notin m_i }
  { \ucons(X\ m_i...m_n, X) }
  \rname{u-constr-x}

@@

\subsection{Linear Constructor}
For some type $C$ and type variable $X$, the judgment $\lcons(C, X)$ is inductively defined over the structure of $C$ as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ X \notin m_i }
  { \lcons(X\ m_i...m_n, X) }
  \rname{l-constr-x} \\

@@

  \inferrule
  { X \notin M \\ activation(C, X) }
  { \lcons((x \ltype M) \rightarrow C, X)}
  \rname{l-constr-arrow-2}
\end{mathpar}
For some type $C$ and type variable $X$, the judgment $activation(C, X)$ is inductively defined over the structure of $C$ as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ X \notin m_i }
  { activation(X\ m_i...m_n, X) }
  \rname{act-x}

@@

\pagebreak

\subsection{Introduction Rules}
The formation of new inductive types is defined as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ arity(A, s) \\ \scons(C_i, X) \\\\
    \pure{\Gamma} \\ 
    \Gamma \vdash A : U_{k+1} \\ 
    \Gamma, X \utype A \vdash C_i : U_k }
  { \Gamma \vdash Ind_s(X : A)\{C_1|...|C_n\} : A }
  \rname{ind-intro}
\end{mathpar}
The formation of constructors for defined inductive types is defined as follows.
\begin{mathpar}
  \inferrule
  { \pure{\Gamma} \\   
    I_s := Ind_s(X : A)\{C_1|...|C_n\} \\
    \Gamma \vdash I_s :A \\
    1 \leq i \leq n }
  { \Gamma \vdash Constr(i, I_s) : C_i[I_s/X] }
  \rname{constr-intro}
\end{mathpar}

\subsection{Non-Dependent Case}
\subsection{Dependent Case}
\subsection{Fixpoint}
\subsection{Examples}

>>>>

\newcommand{\rname}[1]{\textsc{\footnotesize #1}}
\newcommand{\utype}{:_{\scriptscriptstyle U}}
\newcommand{\ltype}{:_{\scriptscriptstyle L}}
\newcommand{\stype}{:_s}
\newcommand{\ucons}{constructor_{\scriptscriptstyle U}}
\newcommand{\lcons}{constructor_{\scriptscriptstyle L}}
\newcommand{\scons}{constructor_{s}}
\newcommand{\indu}{\text{Ind}_{\scriptscriptstyle U}}
\newcommand{\indl}{\text{Ind}_{\scriptscriptstyle L}}
\newcommand{\inds}{\text{Ind}_s}
\newcommand{\constr}{\text{Constr}}
\newcommand{\case}{\text{Case}}
\newcommand{\dcase}{\text{DCase}}
\newcommand{\fix}{\text{Fix }}
\newcommand{\pure}[1]{|#1|}
\newcommand{\mrg}[3]{#1\ddagger#2\ddagger#3}
\newcommand{\restr}[1]{\overline{#1}}
\newcommand{\lrangle}[1]{\langle #1 \rangle}

@@

  \inferrule
  { arity(A, s) }
  { arity((x \utype M) \rightarrow A, s)}
  \rname{ar-arrow}
\end{mathpar}
For some arity type $A$ and sort $s'$, the term $A\lrangle{s'}$ is inductively defined over the structure of $A$ as follows.
\begin{align*}
  ((x \utype M) \rightarrow A)\lrangle{s'} &= (x \utype M) \rightarrow A\lrangle{s'} \\
  (s)\lrangle{s'} &= s'
\end{align*}
For some arity type $A$, term $I$ and sort $s'$, the term $A\{I, s'\}$ is inductively defined over the structure of $A$ as follows.
\begin{align*}
  ((x \utype M) \rightarrow A)\lrangle{I, s'} &= (x \utype M) \rightarrow A\lrangle{(I\ x), s'} \\
  (s)\lrangle{I, s'} &= (\_ \utype I) \rightarrow s'
\end{align*}

\subsection{Strict Positivity}
For some type $P$ and type variable $X$, the judgment $postive(P, X)$ is inductively defined over the structure of $P$ as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ X \notin m_i }
  { postive((X\ m_1...m_n), X) }
  \rname{pos-x}

@@

\subsection{Non-Linear Constructor}
For some type $C$ and type variable $X$, the judgment $\ucons(C, X)$ is inductively defined over the structure of $C$ as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ X \notin m_i }
  { \ucons((X\ m_i...m_n), X) }
  \rname{u-constr-x}

@@

\subsection{Linear Constructor}
For some type $C$ and type variable $X$, the judgment $\lcons(C, X)$ is inductively defined over the structure of $C$ as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ X \notin m_i }
  { \lcons((X\ m_i...m_n), X) }
  \rname{l-constr-x} \\

@@

  \inferrule
  { X \notin M \\ activation(C, X) }
  { \lcons((x \ltype M) \rightarrow C, X)}
  \rname{l-constr-arrow-2}
\end{mathpar}
For some type $C$ and type variable $X$, the judgment $activation(C, X)$ is inductively defined over the structure of $C$ as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ X \notin m_i }
  { activation((X\ m_i...m_n), X) }
  \rname{act-x}

@@

\subsection{Introduction Rules}
The formation of new inductive types is defined as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ arity(A, s) \\ \scons(C_i, X) \\\\
    \pure{\Gamma} \\ 
    \Gamma \vdash A : U_{k+1} \\ 
    \Gamma, X \utype A \vdash C_i : U_k }
  { \Gamma \vdash \inds(X : A)\{C_1|...|C_n\} : A }
  \rname{ind-intro}
\end{mathpar}
The formation of constructors for defined inductive types is defined as follows.
\begin{mathpar}
  \inferrule
  { \pure{\Gamma} \\   
    I := \inds(X : A)\{C_1|...|C_n\} \\
    \Gamma \vdash I :A \\
    1 \leq i \leq n }
  { \Gamma \vdash \constr(i, I) : C_i[I/X] }
  \rname{constr-intro}
\end{mathpar}

\subsection{Non-Dependent Case}
For some constructor type $C$ and type variables $X$ and $Q$, the term $C\{X, Q\}$ is inductively defined over the structure of $C$ as follows.
\begin{align*}
  ((\_ \stype P) \rightarrow C)\{X, Q\} &= (\_ \stype P) \multimap C\{X, Q\} \\
  ((\_ \stype P) \multimap C)\{X, Q\} &= (\_ \stype P) \multimap C\{X, Q\} \\
  ((x \stype M) \rightarrow C)\{X, Q\} &= (x \stype P) \multimap C\{X, Q\} \\
  ((x \stype M) \multimap C)\{X, Q\} &= (x \stype P) \multimap C\{X, Q\} \\
  (X\ m_1...m_n)\{X, Q\} &= (Q\ m_1...m_n)
\end{align*}
We define the notation $C[I, P] := C\{X, Q\}[I/X, P/Q]$.

Inductive objects can be eliminated by a case expression as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ 
    \mrg{\Gamma_1}{\Gamma_2}{\Gamma} \\ 
    arity(A, s) \\
    I := \inds(X : A)\{C_1|...|C_n\} \\\\
    \Gamma_1 \vdash m : (I\ a_1...a_n) \\
    \restr{\Gamma_2} \vdash Q : A\lrangle{s'} \\
    \Gamma_2 \vdash f_i : C_i[I, Q] }
  { \Gamma \vdash \case(m, Q)\{f_1|...|f_n\} : (Q\ a_1...a_n) }
  \rname{case}
\end{mathpar}

\subsection{Dependent Case}
For some non-linear constructor type $C$ and type variables $X$, $Q$ and $c$, the term $C\{X, Q, c\}$ is inductively defined over the structure of $C$ as follows.
\begin{align*}
  ((\_ \utype P) \rightarrow C)\{X, Q, c\} &= (p \utype P) \multimap C\{X, Q, (c\ p)\} \\
  ((x \utype M) \rightarrow C)\{X, Q, c\} &= (x \utype M) \multimap C\{X, Q, (c\ x)\} \\
  (X\ m_1...m_n)\{X, Q, c\} &= (Q\ m_1...m_n\ c)
\end{align*}
We define the notation $C[I, P, t] := C\{X, Q, c\}[I/X, P/Q, t/c]$.

Non-linear inductive objects can be eliminated by a dependent case expression as follows.
\begin{mathpar}
  \inferrule
  { (\forall i = 1...n) \\ 
    \mrg{\Gamma_1}{\Gamma_2}{\Gamma} \\ 
    arity(A, U_i) \\
    I := \indu(X : A)\{C_1|...|C_n\} \\\\
    \Gamma_1 \vdash m : (I\ a_1...a_n) \\
    \restr{\Gamma_2} \vdash Q : A\lrangle{I, s'} \\
    \Gamma_2 \vdash f_i : C_i[I, Q, Constr(i, I)] }
  { \Gamma \vdash \dcase(m, Q)\{f_1|...|f_n\} : (Q\ a_1...a_n) }
  \rname{dcase}
\end{mathpar}

\subsection{Fixpoint}
\begin{mathpar}
  \inferrule
  { \pure{\Gamma} \\ 
    \Gamma \vdash T : U_i \\ 
    \Gamma, f \utype T \vdash m : T \\
    \text{guard condition} }
  { \Gamma \vdash \fix f.m : T }
  \rname{fix}
\end{mathpar}
